Combine filtered data from all three studies in AMP-AD for metanalysis

### 2017-05-07 code/Rmd/combineAllRNASeqData.Rmd
Minor modifications

# Modify ROSMAP covariates
covariates$ROSMAP = covariates$ROSMAP %>%
  dplyr::mutate(Gender = factor(msex, levels = c(0,1), labels = c('0' = 'FEMALE', '1' = 'MALE')),
                RIN = RINcontinuous,
                AAD = age_death,
                PMI = pmi,
                BrainRegion = 'DLPFC',
                Study = 'ROSMAP') %>%
  dplyr::select(SampleID, Study, BrainRegion, Diagnosis, Batch, Gender, RIN, AAD, PMI, PCT_PF_READS_ALIGNED,
                PCT_CODING_BASES, PCT_INTERGENIC_BASES, PCT_INTRONIC_BASES, PCT_RIBOSOMAL_BASES)

# Modify MSBB covariates
covariates$MSBB = covariates$MSBB %>%
  dplyr::mutate(Gender = factor(SEX, levels = c('F', 'M'), labels = c('F' = 'FEMALE', 'M' = 'MALE')),
                Batch = batch,
                PMI = PMI/60,
                AAD = AOD,
                Donor_ID = individualIdentifier,
                Study = 'MSBB') %>%
  tidyr::separate(BrainRegion.Diagnosis, c('BrainRegion', 'Diagnosis'), sep = '\\.') %>%
  dplyr::select(SampleID, Study, BrainRegion, Diagnosis, Batch, Gender, RIN, AAD, PMI, PCT_PF_READS_ALIGNED,
                PCT_CODING_BASES, PCT_INTERGENIC_BASES, PCT_INTRONIC_BASES, PCT_RIBOSOMAL_BASES)

# Modify MAYO covariates
covariates$MAYO = covariates$MAYO %>%
  dplyr::mutate(Gender = factor(Gender, levels = c('F', 'M'), labels = c('F' = 'FEMALE', 'M' = 'MALE')),
                Batch = FLOWCELL,
                AAD = AgeAtDeath,
                Study = factor(Source, 
                               levels = c('BannerSunHealth_TomBeach', 'MayoBrainBank_Dickson'),
                               labels = c('BannerSunHealth_TomBeach' = 'BANNER', 'MAYO'))) %>%
  tidyr::separate(BrainRegion.Diagnosis, c('BrainRegion', 'Diagnosis'), sep = '\\.') %>%
  dplyr::select(SampleID, Study, BrainRegion, Diagnosis, Batch, Gender, RIN, AAD, PMI, PCT_PF_READS_ALIGNED,
                PCT_CODING_BASES, PCT_INTERGENIC_BASES, PCT_INTRONIC_BASES, PCT_RIBOSOMAL_BASES)

@@

p = ggplot(covariates1, aes(x = Diagnosis, y = PCT_INTERGENIC_BASES, color = BrainRegion)) + geom_boxplot()
p
```

@@

# Store raw counts in synapse
write.table(logcpm, file = 'allReprocessedCounts.tsv', sep = '\t', row.names=F, quote=F)
OBJ = File('allReprocessedCounts.tsv', 
           name = 'All RNASeq reprocessed raw counts', 
           parentId = CODE$properties$id)
OBJ = synStore(OBJ,
               used = all.used.ids,
               executed = thisFile,
               activityName = activityName,
               activityDescription = activityDescription)
```
### Source code in github
[Source Code](`r thisFile`)

>>>>

# Modify ROSMAP covariates
rosmap.key = downloadFile('syn3382527') %>%
  dplyr::select(projid, mrna_id) %>%
  tidyr::separate(mrna_id, c('a','b','c'), sep = '_') %>%
  tidyr::unite(SampleID, a,b, sep = '_') %>%
  dplyr::rename(Donor_ID = projid)
all.used.ids = c(all.used.ids, 'syn3382527')

covariates$ROSMAP = covariates$ROSMAP %>%
  left_join(rosmap.key) %>%
  dplyr::mutate(Gender = factor(msex, levels = c(0,1), labels = c('0' = 'FEMALE', '1' = 'MALE')),
                RIN = RINcontinuous,
                AAD = age_death,
                PMI = pmi,
                BrainRegion = 'DLPFC',
                Study = 'ROSMAP') %>%
  dplyr::select(SampleID, Donor_ID, Study, BrainRegion, Diagnosis, Batch, Gender, RIN, AAD, PMI, PCT_PF_READS_ALIGNED,
                PCT_CODING_BASES, PCT_INTERGENIC_BASES, PCT_INTRONIC_BASES, PCT_RIBOSOMAL_BASES)

# Modify MSBB covariates
covariates$MSBB = covariates$MSBB %>%
  dplyr::mutate(Gender = factor(SEX, levels = c('F', 'M'), labels = c('F' = 'FEMALE', 'M' = 'MALE')),
                Batch = batch,
                PMI = PMI/60,
                AAD = AOD,
                Donor_ID = individualIdentifier,
                Study = 'MSBB') %>%
  tidyr::separate(BrainRegion.Diagnosis, c('BrainRegion', 'Diagnosis'), sep = '\\.') %>%
  dplyr::select(SampleID, Donor_ID, Study, BrainRegion, Diagnosis, Batch, Gender, RIN, AAD, PMI, PCT_PF_READS_ALIGNED,
                PCT_CODING_BASES, PCT_INTERGENIC_BASES, PCT_INTRONIC_BASES, PCT_RIBOSOMAL_BASES)

# Modify MAYO covariates
covariates$MAYO = covariates$MAYO %>%
  dplyr::mutate(Gender = factor(Gender, levels = c('F', 'M'), labels = c('F' = 'FEMALE', 'M' = 'MALE')),
                Batch = FLOWCELL,
                AAD = AgeAtDeath,
                Study = factor(Source, 
                               levels = c('BannerSunHealth_TomBeach', 'MayoBrainBank_Dickson'),
                               labels = c('BannerSunHealth_TomBeach' = 'BANNER', 'MAYO'))) %>%
  tidyr::separate(BrainRegion.Diagnosis, c('BrainRegion', 'Diagnosis'), sep = '\\.') %>%
  dplyr::select(SampleID, Donor_ID, Study, BrainRegion, Diagnosis, Batch, Gender, RIN, AAD, PMI, PCT_PF_READS_ALIGNED,
                PCT_CODING_BASES, PCT_INTERGENIC_BASES, PCT_INTRONIC_BASES, PCT_RIBOSOMAL_BASES)

@@

p = ggplot(covariates1, aes(x = Diagnosis, y = PCT_INTERGENIC_BASES, color = BrainRegion)) + geom_boxplot()
p

p = ggplot(covariates1, aes(x = Diagnosis, y = PCT_INTRONIC_BASES, color = BrainRegion)) + geom_boxplot()
p

p = ggplot(covariates1, aes(x = Diagnosis, y = PCT_RIBOSOMAL_BASES, color = BrainRegion)) + geom_boxplot()
p

p = ggplot(covariates1, aes(x = Diagnosis, y = PCT_CODING_BASES, color = BrainRegion)) + geom_boxplot()
p

p = ggplot(covariates1, aes(x = Diagnosis, y = PCT_PF_READS_ALIGNED, color = BrainRegion)) + geom_boxplot()
p
```

@@

# Store raw counts in synapse
write.table(counts, file = 'allReprocessedCounts.tsv', sep = '\t', row.names=F, quote=F)
OBJ = File('allReprocessedCounts.tsv', 
           name = 'All RNASeq reprocessed raw counts', 
           parentId = CODE$properties$id)
OBJ = synStore(OBJ,
               used = all.used.ids,
               executed = thisFile,
               activityName = activityName,
               activityDescription = activityDescription)
```
### Source code in github
[Source Code](`r thisFile`)
